### 2008-08-19 doc/ws-quick-guide/ws-quick-guide.tex
Rename approxy -> arcproxy

ARC comes with utility \texttt{approxy} which generates proxy credentials from
certificate/private key pair. It provides only basic functionality and is meant
for testing purposes only.

@@

then you won't be able to use proxy credentials generated by utilities
like \texttt{grid-proxy-init}, \texttt{voms-proxy-init} or \texttt{approxy}.
Because of that all user private keys will have to be kept unencrypted.
\end{framed}

@@

As metioned above, ARC comes with proxy generation utility
-- \texttt{approxy}, installed in \verb|$ARC_LOCATION/bin|. The usage
of \texttt{approxy} is like:

\begin{lstlisting}
$ARC_LOCATION/bin/approxy -P proxy.pem -C cert.pem -K key.pem
  -c validityStart=2008-05-29T10:20:30Z
  -c validityEnd=2008-06-29T10:20:30Z
  -c proxyPolicyFile=delegation_policy.xml
\end{lstlisting}

>>>>

ARC comes with utility \texttt{arcproxy} which generates proxy credentials from
certificate/private key pair. It provides only basic functionality and is meant
for testing purposes only.

@@

then you won't be able to use proxy credentials generated by utilities
like \texttt{grid-proxy-init}, \texttt{voms-proxy-init} or \texttt{arcproxy}.
Because of that all user private keys will have to be kept unencrypted.
\end{framed}

@@

As metioned above, ARC comes with proxy generation utility
-- \texttt{arcproxy}, installed in \verb|$ARC_LOCATION/bin|. The usage
of \texttt{arcproxy} is like:

\begin{lstlisting}
$ARC_LOCATION/bin/arcproxy -P proxy.pem -C cert.pem -K key.pem
  -c validityStart=2008-05-29T10:20:30Z
  -c validityEnd=2008-06-29T10:20:30Z
  -c proxyPolicyFile=delegation_policy.xml
\end{lstlisting}
